---
title: "Assignment 2"
author: "Irene Cheung"
date: "5/3/2017"
output:
  html_document: default
  pdf_document: default
---
### Q1
```{r}
getwd()
eum_ass<-read.csv("eum_assignment.csv")
head(eum_ass,5)
str(eum_ass)
summary(eum_ass)
```

```{r}
eum_sen<-read.csv("eum_sensrelv.csv")
head(eum_sen,5)
str(eum_sen)
summary(eum_sen)
```
### Merge
```{r}
eum_mer <- merge(eum_ass, eum_sen, by="item")
head(eum_mer,5)
str(eum_mer)
summary(eum_mer)
```
#### Replace the data in a field based on the given value
```{r}
eum_mer$know[eum_mer$know==1] <- "Y"
eum_mer$know[eum_mer$know==2] <- "N"
eum_mer$expr[eum_mer$expr==1] <- "Y"
eum_mer$expr[eum_mer$expr==2] <- "N"
eum_mer$sex[eum_mer$sex==1] <- "male"
eum_mer$sex[eum_mer$sex==2] <- "female"
eum_mer$prov[eum_mer$prov==1] <- "Provided correct information"
eum_mer$prov[eum_mer$prov==2] <- "Not provided correct information"
eum_mer$prov[eum_mer$prov==3] <- "Provided incorrect information"
```

### Distribution who have provided correct information 
```{r}
table.prov=table(eum_mer$prov)
table.prov
table.prov_prop <-table.prov/6090
table.prov_percent<- paste(round(table.prov_prop*100,digits=1),"%",sep="")
table.prov_percent
pie(table.prov)
```
##Descriptive statistics and visualization plot
#### No.of observations that have knowledge on the site regarding how it works
```{r}
library(data.table)
table.know=table(eum_mer$know)
table.know
pie(table.know)
```
#### No.of observations that has expereince of online matchmaking
```{r}
table.expr=table(eum_mer$expr)
table.expr
pie(table.expr)
```
#### No.of observations about Internet Trust
```{r}
table.itr=table(eum_mer$itr)
table.itr
as.data.frame(table(cut(eum_mer$itr, breaks=seq(1,6, by=1))))
hist(eum_mer$itr, 
     main="Internet Trust", 
     xlab="Internet Trust (Likert scale, 6=trust much , 1=dont believe)", 
     border="white", 
     col="lightpink",
     xlim=c(1,6),
     las=1, 
     breaks=5)
```
### No.of observations about Internet privacy concern (Likert scale, 7=high , 1=low)
```{r}
table.ip=table(eum_mer$ip)
table.ip
as.data.frame(table(cut(eum_mer$ip, breaks=seq(1,7, by=1))))
hist(eum_mer$ip, 
     main="Internet Privacy Concern", 
     xlab="Internet Privacy Concern (Likert scale, 7=high , 1=low)", 
     border="white", 
     col="purple",
     xlim=c(1,7),
     las=1, 
     breaks=5)
```
### Age distribution 
```{r}
table.age=table(eum_mer$age)
table.age
as.data.frame(table(cut(eum_mer$age, breaks=seq(18,30, by=2))))
hist(eum_mer$age, 
     main="Age distribution", 
     xlab="Age", 
     border="white", 
     col="green",
     xlim=c(18,30),
     las=1, 
     breaks=5)
```
### Gender distribution 
```{r}
table.sex=table(eum_mer$sex)
table.sex
pie(table.sex)
```
### Info provided distribution 
```{r}
table.prov=table(eum_mer$prov)
table.prov
pie(table.prov)
```

#Sensitivity of informations 
```{r}
table.sen=table(eum_mer$sen)
table.sen
as.data.frame(table(cut(eum_mer$sen, breaks=seq(0,100, by=10))))
hist(eum_mer$sen, 
     main="Sensitivity of informations", 
     xlab="Sensitivity", 
     border="white", 
     col="orange",
     xlim=c(0,100),
     las=1, 
     breaks=5)
```
#Relevant of informations 
```{r}
table.relv=table(eum_mer$relv)
table.relv
as.data.frame(table(cut(eum_mer$relv, breaks=seq(0,100, by=10))))
hist(eum_mer$relv, 
     main="Relevance of informations", 
     xlab="Relevance (0=not at all, 100=extremely relevant)", 
     border="white", 
     col="palegreen",
     xlim=c(0,100),
     las=1, 
     breaks=5)
```
##################
### In order to analysis the data, we excluded the info which is not provided.
### Remove prov==p
```{r}
eum_mer_r<- subset(eum_mer, eum_mer$prov!="Not provided correct information")
str(eum_mer_r)
head(eum_mer_r)
sum(eum_mer_r$prov=="Not provided correct information")
sum(eum_mer_r$prov=="Not provided correct information")
```

#Descriptive statistics and visualization plot after remove info which is not provided.
### No.of observations that have knowledge on the site regarding how it works
```{r}
library(data.table)
table.know_r=table(eum_mer_r$know)
table.know_r
pie(table.know_r)
```
### No.of observations that has expereince of online matchmaking after removed 
```{r}
table.expr_r=table(eum_mer_r$expr)
table.expr_r
pie(table.expr_r)
```
### No.of observations about Internet Trust after removed 
```{r}
table.itr_r=table(eum_mer_r$itr)
table.itr_r
as.data.frame(table(cut(eum_mer_r$itr, breaks=seq(1,6, by=1))))
hist(eum_mer_r$itr, 
     main="Internet Trust after remove", 
     xlab="Internet Trust (Likert scale, 6=trust much , 1=dont believe)", 
     border="white", 
     col="lightpink",
     xlim=c(1,6),
     las=1, 
     breaks=5)
```
### No.of observations about Internet privacy concern (Likert scale, 7=high , 1=low) after removed 
```{r}
table.ip_r=table(eum_mer_r$ip)
table.ip_r
as.data.frame(table(cut(eum_mer_r$ip, breaks=seq(1,7, by=1))))
hist(eum_mer_r$ip, 
     main="Internet Privacy Concern", 
     xlab="Internet Privacy Concern (Likert scale, 7=high , 1=low)", 
     border="white", 
     col="purple",
     xlim=c(1,7),
     las=1, 
     breaks=5)
```
### Age distribution after removed 
```{r}
table.age_r=table(eum_mer_r$age)
table.age_r
as.data.frame(table(cut(eum_mer_r$age, breaks=seq(18,30, by=2))))
hist(eum_mer_r$age, 
     main="Age distribution", 
     xlab="Age", 
     border="white", 
     col="green",
     xlim=c(18,30),
     las=1, 
     breaks=5)
```
### Gender distribution after removed 
```{r}
table.sex_r=table(eum_mer_r$sex)
table.sex_r
pie(table.sex_r)
```
### Info provided distribution after removed 
```{r}
table.prov_r=table(eum_mer_r$prov)
table.prov_r
pie(table.prov_r)
```
### Sensitivity of informations after removed 
```{r}
table.sen_r=table(eum_mer_r$sen)
table.sen_r
as.data.frame(table(cut(eum_mer_r$sen, breaks=seq(0,100, by=10))))
hist(eum_mer_r$sen, 
     main="Sensitivity of informations", 
     xlab="Sensitivity", 
     border="white", 
     col="orange",
     xlim=c(0,100),
     las=1, 
     breaks=5)
```
### Relevant of informations after removed 
```{r}
table.relv_r=table(eum_mer_r$relv)
table.relv_r
as.data.frame(table(cut(eum_mer_r$relv, breaks=seq(0,100, by=10))))
hist(eum_mer_r$relv, 
     main="Relevance of informations", 
     xlab="Relevance (0=not at all, 100=extremely relevant)", 
     border="white", 
     col="palegreen",
     xlim=c(0,100),
     las=1, 
     breaks=5)
```
#######
#Correlation coefficients
```{r}
cov(eum_mer_r$D,eum_mer_r$sen)
cov(eum_mer_r$D,eum_mer_r$relv)
```
################################
#eum_mer$prov[eum_mer$prov==1] <- "Provided correct information"
#eum_mer$prov[eum_mer$prov==2] <- "Not provided correct information"
#eum_mer$prov[eum_mer$prov==3] <- "Provided incorrect information"
#############################
### Generate dummy vars for all 6090 observations 
```{r}
eum_mer$D<-ifelse(eum_mer$prov=="Provided correct information",1,0)
sum(eum_mer$D==1)
sum(eum_mer$D==0)
```
### Generate dummy vars for removed not provided info, 5200 observations 
```{r}
eum_mer_r$D<-ifelse(eum_mer_r$prov=="Provided correct information",1,0)
sum(eum_mer_r$D==1)
sum(eum_mer_r$D==0)
```
### Sensitivity for all 6090 observations
```{r}
t.test(eum_mer$sen[eum_mer$D==1],eum_mer$sen[eum_mer$D==0])
```

### Sensitivity for removed not provided info, 5200 observations 
```{r}
t.test(eum_mer_r$sen[eum_mer_r$D==1],eum_mer_r$sen[eum_mer_r$D==0]) 
```
### Relevant for all observations 6090
```{r}
t.test(eum_mer$relv[eum_mer$D==1],eum_mer$relv[eum_mer$D==0]) 
```
### Relevant for removed "not provide"" observations 
```{r}
t.test(eum_mer_r$relv[eum_mer_r$D==1],eum_mer_r$relv[eum_mer_r$D==0]) 
```

###########
#Q2+Q3
###########
#Generate other dummy vars# 
```{r}
eum_mer_r$K<-ifelse(eum_mer_r$know=="Y",1,0)
eum_mer_r$E<-ifelse(eum_mer_r$expr=="Y",1,0)
head(eum_mer_r)
str(eum_mer_r)
summary(eum_mer_r)
```
#############################
#Pooling Model
Pooling model ignores the unobserved heterogeneity of users, and ignores possible association within users (groups, firms).
#Regress D on sen,relv, K, E, itr, ip, sex, and age.
#Using a simple regression model
```{r}
lmfit<-lm(eum_mer_r$D~eum_mer_r$sen+eum_mer_r$relv+eum_mer_r$K+eum_mer_r$E+eum_mer_r$itr+eum_mer_r$ip+eum_mer_r$sex+eum_mer_r$age)
summary(lmfit)
```
The R-squared is 0.1585, meaning that the model only explains 15.9% of the variability of the response data around its mean. Residual standard error is 0.3944.
Apart from internet privacy concern and age, other six features are identified as being statistically significant (p-value, shown as Pr(>|t|), < .05). Rather than just comparing the numbers in the output, it can be helpful to visualize the coefficients by coefplot package.

```{r}
library(coefplot)
coefplot(lmfit, intercept=FALSE, outerCI=1.96, lwdOuter=1.5,ylab="Rating of Feature",xlab="Association with Overall Satisfaction")
```
#Check the multicollinearity using the VIF
```{r}
library(car)
vif(lmfit)
sqrt(vif(lmfit))>2
```
#Let keep ip and age as they are just control variables.
#Conduct the BP test
```{r}
library(lmtest)
bptest(lmfit)
```
#Employ robust standard errors
```{r}
library(rms)
olsfit=ols(D~sen+relv+K+E+itr+ip+sex+age, data=eum_mer_r, x=TRUE, y=TRUE)
robcov(olsfit)
```
#Use a pooling model
```{r}
library(plm)
eum_mer_r.pl <- plm(D~sen+relv+K+E+itr+ip+sex+age,data=eum_mer_r,model="pooling")
summary(eum_mer_r.pl)
```

To control for the unobserved heterogeneity, we can take the first difference (period-to-period change) and use it for the analysis.
#Use a first-difference model
```{r}
eum_mer_r.fd <- plm(D~sen+relv+K+E+itr+ip+sex+age,data=eum_mer_r,model="fd")
summary(eum_mer_r.fd)
```
# Apply panel models 
# Fixed effect model
```{r}
eum_mer_r.fe <- plm(D~sen+relv+K+E+itr+ip+sex+age,data=eum_mer_r,model="within")
summary(eum_mer_r.fe)
#
fixef(eum_mer_r.fe)
```
# random effect model
```{r}
eum_mer_r.re <- plm(D~sen+relv+K+E+itr+ip+sex+age,data=eum_mer_r,model="random")
summary(eum_mer_r.re)
```
# Conduct hausman test
```{r}
phtest(eum_mer_r.fe, eum_mer_r.re)
```
#Using the panel glm model
```{r}
#install.packages("pglm")
library(pglm)
eum_mer_r.gre<-pglm(D~sen+relv+K+E+itr+ip+sex+age,data=eum_mer_r,family = binomial,index = 'ID',model="random")
summary(eum_mer_r.gre)
```
###########
#Q4
###########
#### Main effect model
```{r}
lmfit1=lm(eum_mer_r$relv~eum_mer_r$sen+eum_mer_r$D)
summary(lmfit1)
```
#### Moderation effect model
```{r}
lmfit2=lm(eum_mer_r$relv~eum_mer_r$sen+eum_mer_r$D+eum_mer_r$sen*eum_mer_r$D)
summary(lmfit2)
```
# Check Model Improvement
# Conduct the Wald test#1
```{r}
library(aod)
wald.test(b=coef(lmfit1), Sigma=vcov(lmfit1), Terms=3)
```

# Conduct the Wald test#2
```{r}
library(aod)
wald.test(b=coef(lmfit2), Sigma=vcov(lmfit2), Terms=4)
```
###########
#Q5
###########
##### We do better to have more data to establish the relationship between D and sen, relv. The possible control variables like citizen, born of country, race and skin colour can incorporate into the model.


