---
title: "Assignment3"
author: "Irene Cheung"
date: "May 12, 2017"
output:
  html_document: default
  word_document: default
---
#### Get and set the current working directory
```{r}
getwd()
```
# Q1
#### Load and subset the data
```{r}
library(foreign)
buy_activity_summary<-read.csv("buy_activity_summary.csv")
head(buy_activity_summary,5)
hero<-subset(buy_activity_summary, app_key==80862143)
head(hero,5)
str(hero)
```
#### Get discriptive statistics
```{r}
summary(hero$no_purcha_days)
mean(hero$no_purcha_days)
sd(hero$no_purcha_days)
#
summary(hero$no_purcha)
mean(hero$no_purcha)
sd(hero$no_purcha)
#
summary(hero$sum_expense)
mean(hero$sum_expense)
sd(hero$sum_expense)
```

#### Draw a histogram


```{r}
hist(hero$no_purcha_days)
# add more cells
hist(hero$no_purcha_days, breaks=100)
#lmit the max of x-axis
hist(hero$no_purcha_days, breaks=100, xlim=c(0,10)) 
hist(hero$no_purcha, breaks=100)
hist(hero$sum_expense, breaks=100, xlim=c(0,1000000))
```
#Q2
#### Find the contribution of high-spenders
#### Defining high-spenders
```{r}
#Whale
hero$is_whale <- ifelse(hero$sum_expense>=1000000, c(1), c(0))
head(hero,5)
#dolphin
hero$is_dolphin <- ifelse(hero$sum_expense>=100000, c(1), c(0))
head(hero,5)
names(hero)
#minnow
hero$is_minnow <- ifelse(hero$sum_expense<100000, c(1), c(0))
head(hero,5)
```


##### purch days no total by class
```{r}
#whale
whale.data=subset(hero, hero$is_whale=="1")
head(whale.data)
summary(whale.data)
str(whale.data)
mean(whale.data$no_purcha_days, na.rm=TRUE)
sd(whale.data$no_purcha_days, na.rm=TRUE)
#dolphin
dolphin.data=subset(hero, hero$is_dolphin=="1")
head(dolphin.data)

str(dolphin.data, na.rm=TRUE)
mean(dolphin.data$no_purcha_days, na.rm=TRUE)
sd(dolphin.data$no_purcha_days, na.rm=TRUE)
#minnow
minnow.data=subset(hero, hero$is_minnow=="1")
head(minnow.data)
str(minnow.data)
mean(minnow.data$no_purcha_days, na.rm=TRUE)
sd(minnow.data$no_purcha_days, na.rm=TRUE)

```


#### Percentile
```{r}
hero$p1 <- ifelse(hero$sum_expense>=quantile(hero$sum_expense, c(.99)), c(1), c(0))
head(hero,5)
hero$p5 <- ifelse(hero$sum_expense>=quantile(hero$sum_expense, c(.95)), c(1), c(0))
head(hero)
hero$p10 <- ifelse(hero$sum_expense>=quantile(hero$sum_expense, c(.90)), c(1), c(0))
head(hero,5)

```
##### we need p1,p5,p10 date
```{r}
head(hero)
var2 <- c("user_no","p1", "p5", "p10")
pdata<- hero[var2]
head(pdata)
```


#### Quantile
```{r}
quantile(hero$sum_expense, c(.99))
quantile(hero$sum_expense, c(.90))
quantile(hero$sum_expense, c(.50))
```
#### Generating descriptive statsitics on each class
```{r}
#install.packages("data.table")
library(data.table)
# whale vs others
dtf <- data.frame(a=hero$sum_expense,b=hero$is_whale)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]
# dolphin vs others
dtf <- data.frame(a=hero$sum_expense,b=hero$is_dolphin)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]
# minnow vs others
dtf <- data.frame(a=hero$sum_expense,b=hero$is_minnow)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]

```
#### Percentile 
```{r}
dtf <- data.frame(a=hero$sum_expense,b=hero$p1)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]
dtf <- data.frame(a=hero$sum_expense,b=hero$p10)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]
```
#### Defining 'class' variable
```{r}
hero$class <- ifelse(hero$sum_expense>=1000000, "whale", "dolphin")
hero$class <- ifelse(hero$sum_expense<100000, "minnow", hero$class)
```

#### Generating descriptive statsitics by class
```{r}
dtf <- data.frame(a=hero$sum_expense,b=hero$class)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=b]
mean(hero$sum_expense)
sd(hero$sum_expense)
```
#### Open "buy_history" and choose 'hero'
```{r}
buy_history<-read.csv("buy_history.csv")
head(buy_history,5)
str(buy_history)
hero_history<-subset(buy_history, app_key==80862143)
head(hero_history,5)
hero_history$class <- ifelse(hero_history$purch_amount_total>=1000000, "whale", "dolphin")
hero_history$class <- ifelse(hero_history$purch_amount_total<100000, "minnow", hero_history$class)
head(hero_history,5)
names(hero_history)
```
#### Generating day_diff variables
```{r}
hero_history$day_diff_0<-hero_history$purch_date1-hero_history$install_date
head(hero_history,5)
hero_history$day_diff_1<-hero_history$purch_date2-hero_history$purch_date1
head(hero_history,5)
hero_history$day_diff_2<-hero_history$purch_date3-hero_history$purch_date2
head(hero_history,5)
```
#### Generating descriptive statsitics by class
```{r}
library(data.table)
dtf <- data.frame(a=hero_history$purch_amount_total,b=hero_history$purch_days_no_total, c=hero_history$sum_price_rev1, 
d=hero_history$sum_price_rev2, e=hero_history$sum_price_rev3, f=hero_history$day_diff_0, g=hero_history$day_diff_1, h=hero_history$day_diff_2,
i=hero_history$class)
dt <- data.table(dtf)
dt[,list(count=sum(a>=0),mean=mean(a),sd=sd(a), sum=sum(a)),by=i]
dt[,list(count=sum(a>=0),mean=mean(b),sd=sd(b), sum=sum(b)),by=i]
dt[,list(count=sum(a>=0),mean1=mean(c),mean2=mean(d), mean3=mean(e)),by=i]
```

```{r}
#Remove NA
dt[,list(count1=sum(a>=0),mean1=mean(c),count2=sum(d>=0,na.rm=TRUE),mean2=mean(d, na.rm=TRUE), count3=sum(e>=0, na.rm=TRUE),mean3=mean(e, na.rm=TRUE)),by=i]
```
#### mean and no of sum_price_rev1, sum_price_rev2 and sum_price_rev3
```{r}
mean(hero_history$sum_price_rev1,na.rm=TRUE)
count=sum(hero_history$sum_price_rev1>=0, na.rm=TRUE)
count

mean(hero_history$sum_price_rev2, na.rm=TRUE)
count=sum(hero_history$sum_price_rev2>=0, na.rm=TRUE)
count

mean(hero_history$sum_price_rev3, na.rm=TRUE)
count=sum(hero_history$sum_price_rev3>=0, na.rm=TRUE)
count
```
#### Generating usage variables (connection)
```{r}
usage_connection_daily<-read.csv("usage_connection_daily.csv")
hero_connection <- subset(usage_connection_daily, app_key==80862143) 
```

#### We need the install date and the first purchase date
```{r}
head(hero,5)
vars <- c("user_no", "install_date", "purch_date1")
#data <- hero[vars]
head(data,5)
```
#### merge 
```{r}
data_m <- merge(data,hero_connection, by="user_no")
data_m<- na.omit(data_m)
data_m$install_date<- na.omit(data_m$install_date)
data_m$purch_date1<- na.omit(data_m$purch_date1)
head(data_m)
str(data_m)
summary(data_m)
```
#### subset data before puchase
```{r}
data_m$date<-as.Date(as.character(data_m$report_date),"%Y%m%d")
head(data_m)
str(data_m)
```
####
```{r}
data_m_s <- subset(data_m, as.Date(data_m$date)< as.Date(data_m$purch_date1))
head(data_m_s)
str(data_m_s)
```
#Q2
#### no_connection_before_purch
```{r}
data_m_s$report_value<- na.omit(data_m_s$report_value)
data_m_s$user_no<-na.omit(data_m_s$user_no)
data_m_s$no_connection_before_purch <- ave(data_m_s$report_value, data_m_s$user_no, FUN = length)
head(data_m_s)
str(data_m_s)
summary(data_m_s)
mean(data_m_s$no_connection_before_purch)
sd(data_m_s$no_connection_before_purch)
names(data_m_s)
```
#### connection_total_before_purch
```{r}
# connection_total_before_purch
data_m_s$connection_total_before_purch <- ave(data_m_s$report_value, data_m_s$user_no, FUN = sum)
head(data_m_s)
summary(data_m_s)
mean(data_m_s$connection_total_before_purch)
sd(data_m_s$connection_total_before_purch)
names(data_m_s)
```
#### freq_connection_before_purch

```{r}
# freq_connection_before_purch
data_m_s$time_to_purch  <- as.Date(as.character.Date(data_m_s$purch_date1))-
                  as.Date(as.character.Date(data_m_s$install_date))+1
head(data_m_s)
data_m_s$time_to_purch <- as.numeric(data_m_s$time_to_purch)
data_m_s$freq_connection_before_purch <- data_m_s$no_connection_before_purch / data_m_s$time_to_purch
head(data_m_s)
summary(data_m_s)
mean(data_m_s$freq_connection_before_purch)
sd(data_m_s$freq_connection_before_purch)
```
#### connection_mean_before_purch
```{r}
data_m_s$connection_mean_before_purch <- ave(data_m_s$report_value, data_m_s$user_no, FUN = mean)
head(data_m_s)
summary(data_m_s)
mean(data_m_s$connection_mean_before_purch)
sd(data_m_s$connection_mean_before_purch)
```

#### connection_var_before_purch
```{r}
data_m_s$report_value<-na.omit(data_m_s$report_value)
data_m_s$user_no<-na.omit(data_m_s$user_no)

data_m_s$connection_var_before_purch <- ave(data_m_s$report_value, data_m_s$user_no, FUN = var)

head(data_m_s)
str(data_m_s)
summary(data_m_s)
mean(data_m_s$connection_var_before_purch,  na.rm=TRUE)
sd(data_m_s$connection_var_before_purch,  na.rm=TRUE)


```
#Generate max connection value
```{r}
library(data.table)
dtf <- data.frame(data_m_s$report_value,data_m_s$user_no)
dt <- data.table(dtf)
dt[,list(max=max(data_m_s$report_value)),by=data_m_s$user_no]
data_m_s$max<-dt

head(data_m_s)
str(data_m_s)
summary(data_m_s)
```

#### connection_increase_before_purch
#### using a user defined function
```{r}
#### User Defined Function
se <- function(x) { sd(x) / sqrt(length(x)) }
se(hero$sum_expense)
se <- function(x) {
  # computes standard error of the mean
  tmp.sd <- sd(x)   # standard deviation
  tmp.N  <- length(x)  # sample size
  tmp.se <- tmp.sd / sqrt(tmp.N)   # std error of the mean
  return(tmp.se)
}
se(hero$sum_expense)
```
#### function for connection_increase_before_purch
```{r}
get.inc <- function(data_m_s){
   n<-dim(data_m_s)[1]
   a<-0
   b<-0
   for(i in 1:ceiling(n/2)) { 
      a<-a+data_m_s$report_value[i]
   }	
   for(j in ceiling(n/2):n) {
      b<-b+data_m_s$report_value[j]
   }
   return(b/a)
}

```
#### sort data by date
```{r}
data_m_s<-data_m_s[order(data_m_s$user_no, data_m_s$date),] 
head(data_m_s)
```
#### apply get.inc by user
```{r}
connection_increase_before_purch <- by(data_m_s,data_m_s$user_no,get.inc)
connection_increase_before_purch[3]

```
#### get unique value (remove the duplicated users)
```{r}
head(data_m_s)
str(data_m_s)
data_m_s_u<-subset(data_m_s, !duplicated(user_no)) 
head(data_m_s_u)
str(data_m_s_u)
```
#### make a new variable
```{r}
data_m_s_u$connection_increase_before_purch<-by(data_m_s,data_m_s$user_no,get.inc)
data_m_s_u$connection_increase_before_purch[mapply(is.infinite, data_m_s_u$connection_increase_before_purch)] <- NA
head(data_m_s_u)
names(data_m_s_u)
summary(data_m_s_u)
str(data_m_s_u)
mean(data_m_s_u$connection_increase_before_purch,  na.rm=TRUE)
sd(data_m_s_u$connection_increase_before_purch,  na.rm=TRUE)

plot(data_m_s_u$connection_increase_before_purch)

```

####  get descriptive statistics
```{r}
# need a review on the connection data
summary(data_m_s_u) 
cor(data_m_s_u[,9:14,17], use="complete.obs")
library(corrplot)
library(gplots)
M<-cor(data_m_s_u[,9:14,17 ], use="complete.obs")
corrplot(M, method="number")
corrplot(M, method="circle")
```
##### Positive correlations are displayed in blue and negative correlations in red color. Color intensity and the size of the circle are proportional to the correlation coefficients. 

#### generating usage variables (session)
#### choose 'hero' from "usage_session_daily" 
```{r}
usage_session_daily<-read.csv("usage_session_daily.csv")
hero_session <- subset(usage_session_daily, app_key==80862143) 
```
#### we need the install date and the first purchase date
```{r}
head(hero)
vars <- c("user_no", "install_date", "purch_date1")
#data<- hero[vars]
head(data)
```
##### merge 
```{r}
data_m_ses<- merge(hero_session, data, by="user_no")
data_m_ses<- na.omit(data_m_ses)
data_m_ses$install_date<- na.omit(data_m_ses$install_date)
data_m_ses$purch_date1<- na.omit(data_m_ses$purch_date1)
head(data_m_ses)
str(data_m_ses)
summary(data_m_ses)
```
####
```{r}
data_m_ses$date<-as.Date(as.character(data_m_ses$report_date),"%Y%m%d")
head(data_m_ses)
str(data_m_ses)
```

##### subset data before puchase
```{r}
data_m_ses_s <- subset(data_m_ses, as.Date(data_m_ses$date)< as.Date(data_m_ses$purch_date1))
head(data_m_ses_s)
str(data_m_ses_s)
```

###### no_usage_before_purch
```{r}
data_m_ses_s$report_value<- na.omit(data_m_ses_s$report_value)
data_m_ses_s$user_no<-na.omit(data_m_ses_s$user_no)
data_m_ses_s$no_usage_before_purch <- ave(data_m_ses_s$report_value, data_m_ses_s$user_no, FUN = length)
head(data_m_ses_s)
summary(data_m_ses_s)
mean(data_m_ses_s$no_usage_before_purch)
sd(data_m_ses_s$no_usage_before_purch)
```

###### usage_total_before_purch
```{r}
data_m_ses_s$usage_total_before_purch <- ave(data_m_ses_s$report_value, data_m_ses_s$user_no, FUN = sum)
head(data_m_ses_s)
summary(data_m_ses_s)
mean(data_m_ses_s$usage_total_before_purch)
sd(data_m_ses_s$usage_total_before_purch)
```
##### freq_usage_before_purch
```{r}
data_m_ses_s$time_to_purch  <- as.Date(as.character.Date(data_m_ses_s$purch_date1))-
                  as.Date(as.character.Date(data_m_ses_s$install_date))+1
head(data_m_ses_s)
```
##Cont'
```{r}
data_m_ses_s$session_mean_before_purch <- ave(data_m_ses_s$report_value, data_m_ses_s$user_no, FUN = mean)
head(data_m_ses_s)
data_m_ses_s$time_to_purch <- as.numeric(data_m_ses_s$time_to_purch)
data_m_ses_s$freq_usage_before_purch <- data_m_ses_s$no_usage_before_purch / data_m_ses_s$time_to_purch
head(data_m_ses_s)
summary(data_m_ses_s)
mean(data_m_ses_s$freq_usage_before_purch)
sd(data_m_ses_s$freq_usage_before_purch)
```


#### session_mean_before_purch
```{r}
data_m_ses_s$session_mean_before_purch <- ave(data_m_ses_s$report_value, data_m_ses_s$user_no, FUN = mean)
head(data_m_ses_s)
summary(data_m_ses_s)
mean(data_m_ses_s$session_mean_before_purch)
sd(data_m_ses_s$session_mean_before_purch)
```
#### session_var_before_purch
```{r}
data_m_ses_s$session_var_before_purch <- ave(data_m_ses_s$report_value, data_m_ses_s$user_no, FUN = var)
head(data_m_ses_s)
summary(data_m_ses_s)
mean(data_m_ses_s$session_var_before_purch, na.rm=TRUE)
sd(data_m_ses_s$session_var_before_purch, na.rm=TRUE)
```

##### usage_increase_before_purch
#### using a user defined function
```{r}
# function for usage_increase_before_purch
head(data_m_ses_s)
get.inc_ses <- function(data_m_ses_s){
   n<-dim(data_m_ses_s)[1]
   a<-0
   b<-0
   for(i in 1:ceiling(n/2)) { 
      a<-a+data_m_ses_s$report_value[i]
   }	
   for(j in ceiling(n/2):n) {
      b<-b+data_m_ses_s$report_value[j]
   }
   return(b/a)
}
```
#### sort data by date
```{r}
data_m_ses_s<-data_m_ses_s[order(data_m_ses_s$user_no, data_m_ses_s$date),] 
head(data_m_ses_s)
```
#### apply get.inc_ses by user
```{r}
usage_increase_before_purch <- by(data_m_ses_s,data_m_ses_s$user_no,get.inc_ses)
usage_increase_before_purch[3]
```

### get unique value (remove the duplicated users)
```{r}
head(data_m_ses_s)
data_m_ses_s_u<-subset(data_m_ses_s, !duplicated(user_no)) 
head(data_m_ses_s_u)
```
#### make a new variable
```{r}
data_m_ses_s_u$usage_increase_before_purch<-by(data_m_ses_s,data_m_ses_s$user_no,get.inc_ses)
head(data_m_ses_s_u)

summary(data_m_ses_s_u)
mean(data_m_ses_s_u$usage_increase_before_purch)
sd(data_m_ses_s_u$usage_increase_before_purch)


```
##### get descriptive statistics
#### need a review on the session data
```{r}
summary(data_m_ses_s_u)
cor(data_m_ses_s_u[,9:14,17], use="complete.obs")
library(corrplot)
library(gplots)
M1<-cor(data_m_ses_s_u[,9:14,17], use="complete.obs")
corrplot(M1, method="number")
corrplot(M1, method="circle")

```

##### Positive correlations are displayed in blue and negative correlations in red color. Color intensity and the size of the circle are proportional to the correlation coefficients. 
################################################
#Q3
```{r}
#### We need is_dolphin information
names(hero)
var4 <- c("X","app_key","user_no", "report_date","no_purcha_days", "no_purcha","sum_expense","is_whale","is_dolphin", "is_minnow","p1","p5","p10","class")
hero_is<- hero[var4]
head(hero_is,5)
summary(hero_is)
```

```{r}
#### We need the connection_before_purch information
names(data_m_s_u)
var1 <- c("user_no","no_connection_before_purch", "connection_total_before_purch", "time_to_purch", "freq_connection_before_purch","connection_mean_before_purch","connection_var_before_purch","connection_increase_before_purch")
data_m_s_u_use <- data_m_s_u[var1]
head(data_m_s_u_use,5)
```
#
```{r}
#### merge 
#names (hero_history)
final_hero1 <- merge(hero_is,hero_connection, by="user_no")
names(final_hero1)
#summary(final_hero1)
final_hero2<- merge(final_hero1,data_m_s_u_use, by="user_no")
names(final_hero2)
#summary(final_hero2)
final_hero3<- merge(final_hero2,pdata, by="user_no")
names(final_hero3)
summary(final_hero3)
final_hero3<- na.omit(final_hero3)
#data_m$install_date<- na.omit(data_m$install_date)
names(final_hero3)
head(final_hero3)
str(final_hero3)
summary(final_hero3)
```
##Use the rpart function to build a classification tree model
#recursive partitioning A
```{r}
#names(final_hero3)
library(rpart)
library(partykit)
#ds$sub = as.factor(ds$substance)
is_dolphin.rpart = rpart(is_dolphin ~ sum_expense+no_purcha+report_date.y+ report_value, method="class", data=final_hero3)
#Visualization
plot(is_dolphin.rpart, margin=0.1)
text(is_dolphin.rpart, all=TRUE, use.n=TRUE)
#
printcp(is_dolphin.rpart)
plotcp(is_dolphin.rpart)
summary(is_dolphin.rpart)
plot(as.party(is_dolphin.rpart), type="simple")
#
predictions = predict(is_dolphin.rpart, final_hero3, type="class")
table(final_hero3$is_dolphin, predictions)
#Generate a confusion matrix
library(caret)
confusionMatrix(table(final_hero3$is_dolphin, predictions))
```
#Min cross-validation error of the classification tree model
```{r}
min(is_dolphin.rpart$cptable[,"xerror"])
```
#Locate min cross-validation error
```{r}
which.min(is_dolphin.rpart$cptable[,"xerror"])
```
#Get cost complexity parameter of the record with min cross-validation error
```{r}
is_dolphin.cp= is_dolphin.rpart$cptable[2,"CP"]
is_dolphin.cp
```
#Prune the tree by setting CP parameter to CP value
```{r}
prune.tree= prune(is_dolphin.rpart, cp=is_dolphin.cp)
```
#
```{r}
plot(prune.tree, margin(0.1))
text(prune.tree, all=TRUE, use.n=TRUE)
```
##recursive partitioning B--connection info
```{r}
#names(final_hero3)
library(rpart)
library(partykit)
is_dolphin.rpart = rpart(is_dolphin ~ no_connection_before_purch +no_purcha+connection_total_before_purch+ freq_connection_before_purch +connection_mean_before_purch + connection_var_before_purch + connection_increase_before_purch, method="class", data=final_hero3)
plot(is_dolphin.rpart, margin=0.1)
text(is_dolphin.rpart, all=TRUE, use.n=TRUE)
#
printcp(is_dolphin.rpart)
plotcp(is_dolphin.rpart)
summary(is_dolphin.rpart)
plot(as.party(is_dolphin.rpart), type="simple")
#
predictions = predict(is_dolphin.rpart, final_hero3, type="class")
table(final_hero3$is_dolphin, predictions)
#Generate a confusion matrix
library(caret)
confusionMatrix(table(final_hero3$is_dolphin, predictions))
```

#Min cross-validation error of the classification tree model
```{r}
min(is_dolphin.rpart$cptable[,"xerror"])
```
#Locate min cross-validation error
```{r}
which.min(is_dolphin.rpart$cptable[,"xerror"])
```
#
```{r}
#Get cost complexity parameter of the record with min cross-validation error
is_dolphin.cp= is_dolphin.rpart$cptable[2,"CP"]
is_dolphin.cp
```
#Prune the tree by setting CP parameter to CP value
```{r}
prune.tree= prune(is_dolphin.rpart, cp=is_dolphin.cp)
```
#
```{r}
plot(prune.tree, margin(0.1))
text(prune.tree, all=TRUE, use.n=TRUE)
```


```{r}
names(final_hero3)
library(party)
library(partykit)
library(rpart)
library(C50)
library(foreign)
# confirm Data
names(final_hero3)
```

#new
```{r}
##########################################################
#   
# Conditional Inference Tree (final_hero3)
#
##########################################################

# Conditional Tree for M1A
# sum expense & connection info
M1A<-final_hero3[,c(7,18:20,22:25)] 
user_class<-ordered(final_hero3[,c(14)],levels = c("minnow", "dolphin", "whale"))
fit <- ctree(user_class~., data=M1A)
fit
fit<- na.omit(fit)
png(file="C:/Users/Irene/Desktop/R1/M1A_level.png",width=3500,height=800)
plot(fit, main="Conditional Inference Tree for M1-A")
dev.off()
```
#
```{r}
# Conditional Tree for M1-B
#report_date,no purcha days and no purcha
M1B<-final_hero3[,c(4:6)] 
user_class<-ordered(final_hero3[,c(14)],levels = c("minnow", "dolphin", "whale"))
fit <- ctree(user_class~., data=M1B)
fit
fit<- na.omit(fit)
png(file="C:/Users/Irene/Desktop/R1/M1B_level.png",width=3500,height=800)
plot(fit, main="Conditional Inference Tree for M1-B")
dev.off()
```
#
```{r}
# Conditional Tree for M1-C
#p1, p5 & p10
M1C<-final_hero3[,c(11:13)] # 

user_class<-ordered(final_hero3[,c(14)],levels = c("minnow", "dolphin", "whale"))
fit <- ctree(user_class~., data=M1C)
fit
fit<- na.omit(fit)
png(file="C:/Users/Irene/Desktop/R1/M1C_level.png",width=3500,height=800)
plot(fit, main="Conditional Inference Tree for M1-C")
dev.off()
```
#
```{r}
# Conditional Tree for M1-D
#report date & report value, GOOD
M1D<-final_hero3[,c(17:18)] 

user_class<-ordered(final_hero3[,c(14)],levels = c("minnow", "dolphin", "whale"))
fit <- ctree(user_class~., data=M1D)
fit
fit<- na.omit(fit)
png(file="C:/Users/Irene/Desktop/R1/M1D_level.png",width=3500,height=800)
plot(fit, main="Conditional Inference Tree for M1-D")
dev.off()
```
#new
```{r}
##########################################################
#
# 	Logit for M1A
#
##########################################################
library(LOGIT)
names(final_hero3)
summary(final_hero3)
M1A_logit<-final_hero3[,c(9,20,22:25)]  # connection & session_max
#logit <- glm(M1A_logit$is_dolphin. , data = M1A_logit, family = "binomial")
logit <- glm(is_dolphin~. , data = M1A_logit, family = "binomial")
summary(logit)
predict.logit<-predict.glm(logit, newdata=M1A_logit, type="response", se.fit=FALSE) 
pred<-prediction(predict.logit, M1A_logit$is_dolphin, label.ordering = NULL)
M1A_logit$prob <- predict.logit
```
#
```{r}
# ROC curve
tpr_fpr.perf <- performance(pred, measure="tpr", x.measure="fpr")
plot(tpr_fpr.perf)
abline(a=0, b= 1)
```
#
```{r}
# AUC 
auc.perf = performance(pred, measure = "auc")
auc.perf@y.values
```
#
```{r}
# Optimal Cutoff Point
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(tpr_fpr.perf, pred))
```
#M1B
```{r}
# Logit for M1B (report date and report value)

names(final_hero3)
summary(final_hero3)
M1B_logit<-final_hero3[,c(9, 17:18)] 
logit <- glm(is_dolphin~. , data = M1B_logit, family = "binomial")
summary(logit)
predict.logit<-predict.glm(logit, newdata=M1B_logit, type="response", se.fit=FALSE) 
pred<-prediction(predict.logit, M1B_logit$is_dolphin, label.ordering = NULL)
M1B_logit$prob <- predict.logit

```
#### ROC curve for M1B (report date and report value)
```{r}
tpr_fpr.perf <- performance(pred, measure="tpr", x.measure="fpr")
plot(tpr_fpr.perf)
abline(a=0, b= 1)
```
##### AUC for M1B (report date and report value)
```{r}
auc.perf = performance(pred, measure = "auc")
auc.perf@y.values
```
####
```{r}
# Optimal Cutoff Point
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(tpr_fpr.perf, pred))

```
##M1C
```{r}
# Logit for M1C (p1,p2,p3)
names(final_hero3)
summary(final_hero3)
M1C_logit<-final_hero3[,c(9, 11:13)] 
logit <- glm(is_dolphin~. , data = M1C_logit, family = "binomial")
summary(logit)
predict.logit<-predict.glm(logit, newdata=M1C_logit, type="response", se.fit=FALSE) 
pred<-prediction(predict.logit, M1C_logit$is_dolphin, label.ordering = NULL)
M1C_logit$prob <- predict.logit

```
##### ROC curve for M1C (p1,p5,p10)
```{r}
tpr_fpr.perf <- performance(pred, measure="tpr", x.measure="fpr")
plot(tpr_fpr.perf)
abline(a=0, b= 1)
```
#
```{r}
# AUC 
auc.perf = performance(pred, measure = "auc")
auc.perf@y.values
```
#
```{r}
# Optimal Cutoff Point
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x-0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(tpr_fpr.perf, pred))

```

