---
title: "Final Project v.0.1"
author: "Irene Cheung"
date: "June 10, 2017"
output:
  word_document: default
  html_document: default
---

```{r}
#Set working directory
getwd()
setwd("/Users/irene/Desktop/R1")
getwd()
```

```{r}
#Load data
skype<-read.table("skype_student.csv", header=TRUE, sep=",")
str(skype)
head(skype)
names(skype)
```
##### Descriptive statistics on each class
```{r}
library(data.table)
dtsky <- data.table(skype)
summary(dtsky)
str(dtsky)
```
##### Distribution who have provided correct information on Name
```{r}
#(i)Name
dtsky[,list(count=sum(Rname>=0),mean=mean(Rname),sd=sd(Rname)),by=Iname]
dtsky[,list(count=sum(Sname>=0),mean=mean(Sname),sd=sd(Sname)),by=Iname]

```
##### (ii)Email
```{r}
dtsky[,list(count=sum(Remail>=0),mean=mean(Remail),sd=sd(Remail)),by=Iemail]
dtsky[,list(count=sum(Semail>=0),mean=mean(Semail),sd=sd(Semail)),by=Iemail]
```
##### (iii)birthday
```{r}
dtsky[,list(count=sum(Rbirth>=0),mean=mean(Rbirth),sd=sd(Rbirth)),by=Ibirth]
dtsky[,list(count=sum(Sbirth>=0),mean=mean(Sbirth),sd=sd(Sbirth)),by=Ibirth]
```
##### (iv)gender
```{r}
dtsky[,list(count=sum(Rgender>=0),mean=mean(Rgender),sd=sd(Rgender)),by=Igender]
dtsky[,list(count=sum(Sgender>=0),mean=mean(Sgender),sd=sd(Sgender)),by=Igender]
```
## (v)nation
```{r}
dtsky[,list(count=sum(Rnation>=0),mean=mean(Rnation),sd=sd(Rnation)),by=Ination]
dtsky[,list(count=sum(Snation>=0),mean=mean(Snation),sd=sd(Snation)),by=Ination]
```
##### (Vi)city
```{r}
dtsky[,list(count=sum(Rcity>=0),mean=mean(Rcity),sd=sd(Rcity)),by=Icity]
dtsky[,list(count=sum(Scity>=0),mean=mean(Scity),sd=sd(Scity)),by=Icity]
```
#### (vii) language
```{r}
dtsky[,list(count=sum(Rlang>=0),mean=mean(Rlang),sd=sd(Rlang)),by=Ilang]
dtsky[,list(count=sum(Slang>=0),mean=mean(Slang),sd=sd(Slang)),by=Ilang]
```
#### (viii)cellphone number
```{r}
dtsky[,list(count=sum(Rcell>=0),mean=mean(Rcell),sd=sd(Rcell)),by=Icell]
dtsky[,list(count=sum(Scell>=0),mean=mean(Scell),sd=sd(Scell)),by=Icell]
```
#### (ix) purpose
```{r}
dtsky[,list(count=sum(Rpurp>=0),mean=mean(Rpurp),sd=sd(Rpurp)),by=Ipurp]
dtsky[,list(count=sum(Spurp>=0),mean=mean(Spurp),sd=sd(Spurp)),by=Ipurp]
```
##### generating dummies
```{r}
dtsky$Dname<-ifelse(dtsky$Iname==1,1,0)
dtsky$Demail<-ifelse(dtsky$Iemail==1,1,0)
dtsky$Dbirth<-ifelse(dtsky$Ibirth==1,1,0)
dtsky$Dgender<-ifelse(dtsky$Igender==1,1,0)
dtsky$Dnation<-ifelse(dtsky$Ination==1,1,0)
dtsky$Dcity<-ifelse(dtsky$Icity==1,1,0)
dtsky$Dlang<-ifelse(dtsky$Ilang==1,1,0)
dtsky$Dcell<-ifelse(dtsky$Icell==1,1,0)
dtsky$Dpurp<-ifelse(dtsky$Ipurp==1,1,0)
head(dtsky)
```

##### t-test
```{r}
#Name
t.test(dtsky$Rname~dtsky$Dname)
t.test(dtsky$Sname~dtsky$Dname)
```
#
```{r}
#### Correlation coefficients on Name
cov(dtsky$Rname,dtsky$Dname)
cov(dtsky$Sname,dtsky$Dname)
```

```{r}
#Email
t.test(dtsky$Remail~dtsky$Demail)
t.test(dtsky$Semail~dtsky$Demail)
```
#
```{r}
#### Correlation coefficients on Email
cov(dtsky$Remail,dtsky$Demail)
cov(dtsky$Semail,dtsky$Demail)
```

#
```{r}
#Birth
t.test(dtsky$Rbirth~dtsky$Dbirth)
t.test(dtsky$Sbirth~dtsky$Dbirth)
```
#
```{r}
#### Correlation coefficients on Birth
cov(dtsky$Rbirth, dtsky$Dbirth)
cov(dtsky$Sbirth, dtsky$Dbirth)
```

```{r}
#Gender
t.test(dtsky$Rgender~dtsky$Dgender)
t.test(dtsky$Sgender~dtsky$Dgender)
```
#
```{r}
#### Correlation coefficients on Gender
cov(dtsky$Rgender,dtsky$Dgender)
cov(dtsky$Sgender,dtsky$Dgender)
```

```{r}
#Nation
t.test(dtsky$Rnation~dtsky$Dnation)
t.test(dtsky$Snation~dtsky$Dnation)
```
#
```{r}
#### Correlation coefficients on Nation
cov(dtsky$Rnation,dtsky$Dnation)
cov(dtsky$Snation,dtsky$Dnation)
```

```{r}
#City
t.test(dtsky$Rcity~dtsky$Dcity)
t.test(dtsky$Scity~dtsky$Dcity)
```
#
```{r}
#### Correlation coefficients on City
cov(dtsky$Rcity,dtsky$Dcity)
cov(dtsky$Scity,dtsky$Dcity)
```

```{r}
#Language
t.test(dtsky$Rlang~dtsky$Dlang)
t.test(dtsky$Slang~dtsky$Dlang)
```
#
```{r}
#### Correlation coefficients on Language
cov(dtsky$Rlang,dtsky$Dlang)
cov(dtsky$Slang,dtsky$Dlang)
```

```{r}
#Cellphone
t.test(dtsky$Rcell~dtsky$Dcell)
t.test(dtsky$Scell~dtsky$Dcell)
```
#
```{r}
#### Correlation coefficients on Cellphone
cov(dtsky$Rcell,dtsky$Dcell)
cov(dtsky$Scell,dtsky$Dcell)
```

```{r}
#Purpose
t.test(dtsky$Rpurp~dtsky$Dpurp)
t.test(dtsky$Spurp~dtsky$Dpurp)
```

#
```{r}
#### Correlation coefficients on purpose
cov(dtsky$Rpurp,dtsky$Dpurp)
cov(dtsky$Spurp,dtsky$Dpurp)
```
#####################
```{r}
#Load data, skype_student2.csv
skype2<-read.table("skype_student2.csv", header=TRUE, sep=",")
str(skype2)
head(skype2)
names(skype2)
```
#
```{r}
#Remove expl==p
skype2_r <- subset(skype2, expl!="P")
str(skype2_r)
head(skype2_r)
names(skype2_r)
```
#
```{r}
#Generate dummy vars
skype2_r$D<-ifelse(skype2_r$I==1,1,0)
skype2_r$E<-ifelse(skype2_r$expl=="Y",1,0)
skype2_r$M<-ifelse(skype2_r$mand=="Y",1,0)
skype2_r$P<-ifelse(skype2_r$prek=="Y",1,0)
skype2_r$EX<-ifelse(skype2_r$expr=="Y",1,0)
head(skype2_r)
names(skype2_r)
```
######Testing Group Means by t test, It compares the mean for two groups which the user provides the correct and incorrect information on the item
```{r}
t.test(skype2_r$D==1,skype2_r$D==0) 
sum(skype2_r$D==1)
sum(skype2_r$D==0)
```

#(I)Mandatory and Explanation
```{r}
sum(skype2_r$M==0)
sum(skype2_r$M==1)
#
skype2_r$M1_E1=0
skype2_r$M1_E1=as.numeric(skype2_r$M=="1"&skype2_r$E=="1", 1,0)
sum(skype2_r$M1_E1==1)
```
#(II) Mandatory and NO Explanation
```{r}
skype2_r$M1_E0=0
skype2_r$M1_E0=as.numeric(skype2_r$M=="1"&skype2_r$E=="0", 1,0)
sum(skype2_r$M1_E0==1)
```
#(III) Voluntary and Explanation
```{r}
skype2_r$M0_E1=0
skype2_r$M0_E1=as.numeric(skype2_r$M=="0"&skype2_r$E=="1", 1,0)
sum(skype2_r$M0_E1==1)
```
#(IV) Voluntary and No Explanation
```{r}
skype2_r$M0_E0=0
skype2_r$M0_E0=as.numeric(skype2_r$M=="0"&skype2_r$E=="0", 1,0)
sum(skype2_r$M0_E0==1)
```

#Mandatory and Explanation that user provides correct info
```{r}
skype2M1E1.data=subset(skype2_r, skype2_r$M1_E1=="1")
#head(skype2M0E0.data)
#str(skype2M0E0.data)
sum(skype2M1E1.data$D==1)
sum(skype2M1E1.data$D==0)
```
#Mandatory and No Explanation that user provides correct info
```{r}
skype2M1E0.data=subset(skype2_r, skype2_r$M1_E0=="1")
sum(skype2M1E0.data$D==1)
sum(skype2M1E0.data$D==0)
```
##(III) Voluntary and Explanation that user provides correct info

```{r}
skype2M0E1.data=subset(skype2_r, skype2_r$M0_E1=="1")
sum(skype2M0E1.data$D==1)
sum(skype2M0E1.data$D==0)
```
##(IV) Voluntary and NO Explanation that user provides correct info
```{r}
skype2M0E0.data=subset(skype2_r, skype2_r$M0_E0=="1")
sum(skype2M0E0.data$D==1)
sum(skype2M0E0.data$D==0)
```

```{r}
#explanation vs user provides the correct information
t.test(skype2_r$D~skype2_r$E)
cor.test(skype2_r$D, skype2_r$E)
```
#
```{r}
#make all items vs user provides the correct information
t.test(skype2_r$D~skype2_r$M)
cor.test(skype2_r$D, skype2_r$M)
```
#
```{r}
#the user has the knowledge on Skype vs user provides the correct information
t.test(skype2_r$D~skype2_r$P)
cor.test(skype2_r$D, skype2_r$P)
```
#
```{r}
#the user has the direct or indirect experience of using Skype before vs user provides the correct information
t.test(skype2_r$D~skype2_r$EX)
cor.test(skype2_r$D, skype2_r$EX)
```
#
```{r}
#user privacy concerns by using Skype vs user provides the correct information
t.test(skype2_r$D~skype2_r$EX)
cor.test(skype2_r$D, skype2_r$EX)
```
#
merge
```{r}
#### We need PC information
names(skype)
var1 <- c("PC1","PC2","PC3", "ID")
skype_pc<- skype[var1]
skype3 <- merge(skype2_r, skype_pc, by="ID")
head(skype3)
names(skype3)
```

```{r}
anova(aov(skype3$D ~ skype3$PC1+skype3$PC2+skype3$PC3, data=skype3))
cor.test(skype3$D, skype3$PC1)
cor.test(skype3$D, skype3$PC2)
cor.test(skype3$D, skype3$PC3)
#
#head(skype3)
names(skype3)
library(corrplot)
sky0 <-cor(skype3[10:20])
corrplot(sky0, method="circle")
```

#

##### Pooling Model
Pooling model ignores the unobserved heterogeneity of users, and ignores possible association within users (groups, firms).
#### Regress D on R,S,E,M,P,EX,sex, and age.
#### Using a simple regression model
```{r}
#lm 
lmfit<-lm(skype2_r$D~skype2_r$R+skype2_r$S+skype2_r$E+skype2_r$M+skype2_r$P+skype2_r$EX+skype2_r$gender+skype2_r$age)
summary(lmfit)
```
#### coefplot
```{r}
library(coefplot)
coefplot(lmfit, intercept=FALSE, outerCI=1.96, lwdOuter=1.5,ylab="Rating of Feature",xlab="Association with Overall Satisfaction")
```
##### Check the multicollinearity using the VIF
```{r}
library(car)
vif(lmfit)
sqrt(vif(lmfit))>2

```
#### Let keep P, EX, gender and age as they are just control variables.
#### Conduct the BP test
```{r}
library(lmtest)
bptest(lmfit)
```
#### Employ robust standard errors
```{r}
library(rms)
olsfit=ols(D~R+S+E+M+P+EX+gender+age, data=skype2_r, x=TRUE, y=TRUE)
robcov(olsfit)
```
#### Use a pooling model
```{r}
library(plm)
skype.pl <- plm(D~R+S+E+M+P+EX+gender+age, data=skype2_r,model="pooling")
summary(skype.pl)
```
To control for the unobserved heterogeneity, we can take the first difference (period-to-period change) and use it for the analysis.
#### Use a first-difference model
```{r}
skype.fd <- plm(D~R+S+E+M+P+EX+gender+age, data=skype2_r,model="fd")
summary(skype.fd)
```
#### Apply panel models 
#### Fixed effect model
```{r}
skype.fe <- plm(D~R+S+E+M+P+EX+gender+age,data=skype2_r,model="within")
summary(skype.fe)
#
fixef(skype.fe)
```
##### random effect model
```{r}
skype.re <- plm(D~R+S+E+M+P+EX+gender+age,data=skype2_r,model="random")
summary(skype.re)
```
#### Conduct hausman test
```{r}
phtest(skype.fe, skype.re)
```
#### Using the panel glm model
```{r}
#install.packages("pglm")
library(pglm)
skype.gre<-pglm(D~R+S+E+M+P+EX+gender+age,data=skype2_r,family = binomial,index = 'ID',model="random")
summary(skype.gre)
```
#############################
#####Interaction effects
#### Main effect model
```{r}
lmfit1=lm(skype2_r$R~skype2_r$S+skype2_r$D)
summary(lmfit1)
```
#### Moderation effect model
```{r}
lmfit2=lm(skype2_r$R~skype2_r$S+skype2_r$D+skype2_r$S*skype2_r$D)
summary(lmfit2)
```
#### Check Model Improvement
#### Conduct the Wald test#1
```{r}
library(aod)
wald.test(b=coef(lmfit1), Sigma=vcov(lmfit1), Terms=3)
```
#### Conduct the Wald test#2
```{r}
library(aod)
wald.test(b=coef(lmfit2), Sigma=vcov(lmfit2), Terms=4)
```
#### Main effect of R on the relationship between D and S with testing Mutliple Group Means by ANOVA
```{r}
anova(aov(skype2_r$R ~ skype2_r$S+skype2_r$D, data=skype2_r))
```
The result indicate that D is significant predictor (p = 3.577e-10 ). 
##### Main effect and Interaction effect of R on the relationship between D and S with testing Mutliple Group Means by ANOVA.
```{r}
anova(aov(skype2_r$R ~ skype2_r$S* skype2_r$D, data=skype2_r))
```
Again, we found that D is significant predictor (p = 3.634e-10 ).
#############################
#### Model Comparision in ANOVA
#############################
```{r}
anova(aov(skype2_r$R ~ skype2_r$S, data=skype2_r),aov(skype2_r$R ~ skype2_r$S + skype2_r$D, data=skype2_r), aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E, data=skype2_r), aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E +skype2_r$M, data=skype2_r), aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E +skype2_r$M + skype2_r$P, data=skype2_r),aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E +skype2_r$M + skype2_r$P +skype2_r$EX, data=skype2_r), aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E +skype2_r$M + skype2_r$P +skype2_r$EX +skype2_r$gender,data=skype2_r), aov(skype2_r$R ~ skype2_r$S + skype2_r$D+skype2_r$E + skype2_r$M+ skype2_r$P +skype2_r$EX +skype2_r$gender +skype2_r$age ,data=skype2_r) )
```
We found that Model 2 and 5 are are significantly different in overall fit from Model 1. 
#######################
###### We do better to have more data to establish the relationship between D and S, R. The possible control variables like Nation, City and preferred language can incorporate into the model.
